\chapter*{Abstract}
\label{chap:abstract}
\addcontentsline{toc}{chapter}{\nameref{chap:abstract}}

In modern surveillance environments, tracking individuals across multiple camera views presents significant challenges for security personnel, leading to inefficiencies and potential security gaps. The motivation behind this project is to reduce the cognitive burden on operators who must manually monitor numerous video feeds simultaneously while maintaining situational awareness. The \usevar{\srsTitle} addresses the fragmentation of surveillance data across distributed camera networks, as this information typically exists in isolated feeds without meaningful integration. While camera networks may capture comprehensive coverage of physical spaces, without intelligent automation to connect these perspectives, security teams struggle with rapid identification and tracking of persons of interest. Our system proposes a solution through an AI-powered approach that seamlessly identifies and tracks individuals across camera transitions and visualizes movement patterns, with optional advanced query capabilities for enhanced usability. The effectiveness of our solution is evaluated through real-world deployment scenarios under varying environmental conditions. We expect our project to significantly enhance operational efficiency for security personnel while providing more timely and accurate situational awareness. We believe that intelligent automation of cross-camera tracking will transform how organizations approach surveillance and security operations.

\par
\textit{\textbf{Keywords}---Multi-Camera Tracking, Person Re-Identification, Computer Vision, Real-Time Analytics, Situational Awareness, Security Automation}